---
title: "lab_report_knapsack"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab_report_knapsack}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, results=FALSE}
library(knapsack)
```
## The knapsack problem
The knapsack problem is a discrete optimization problem where we have a knapsack that can take a limited weight W and we want to fill this knapsack with a number of items i = 1, ..., n, each with a weight w[i] and a value v[i]. The goal is to find the knapsack with the largest value of the elements added to the knapsack.

### Brute force search
The only solution that is guaranteed to give a correct answer in all situations for the knapsack problem is using brute-force search, i.e. going through all possible alternatives and return the maximum value found.
This can be done using the brute_force_knapsack() function.
```{r}
# creating the knapsack
set.seed(42)
n <- 2000
knapsack_objects <- data.frame(w = sample(1:4000, size = n, replace = TRUE), 
                               v = runif(n = n, 0, 10000))

brute_force_knapsack(x = knapsack_objects[1:8, ], W = 3500)
brute_force_knapsack(x = knapsack_objects[1:12,], W = 3500)
brute_force_knapsack(x = knapsack_objects[1:8,], W = 2000)
brute_force_knapsack(x = knapsack_objects[1:12,], W = 2000)
```
Note that the examples only evaluates maximum 12 knapsack objects. This is because the calculation quickly gets very heavy. The algorithm evaluates all possible combinations. The number of possible combinations is two to the power of the number of knapsack objects, so for a knapsack of size 12 there are 2^12 = 4096 different combinations to be evaluated. Running the code with x = knapsack_objects[1:16, ] took 130 seconds for the authors, however with x = knapsack_objects[1:17, ] this time increased to 13 minutes.

### Greedy heuristic
Another approach is to use a heuristic or approximation for the problem. This algorithm will not give an exact result (but it can be shown that it will return at least 50 % of the true maximum value), but it will reduce the computational complexity considerably.
This is done with the greedy_knapsack() function.
```{r}
# greedy_knapsack(x = knapsack_objects[1:800,], W = 3500)
# greedy_knapsack(x = knapsack_objects[1:1200,], W = 2000)
```


Question How much time does it take to run the algorithm for n = 1000000 objects?
